Reassessing the Impact of Dynamic Slicing in SFL

### 2019-02-09 paper/ijcai/paper.tex
intro pass

%% \author{
%% First Author$^1$,
%% Second Author$^2$,
%% \\ 
%% $^1$ First Affiliation\\
%% $^2$ Second Affiliation\\
%% %
%% first@email.address,
%% second@email.address,
%% third@email.address
%% }

@@

\begin{document}

@@

Dynamic Slicing (\ds{}) and Spectrum-Based Fault Localization (\sfl{})
are two very popular techniques that use different principles to
automate debugging. Dynamic
Slicing~\cite{Agrawal:1990:DPS:93542.93576} looks for the statements
in code that influence some point of interest, such as the evaluation
of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
does not analyze code. It is a black-box statistical fault
localization method that computes suspiciousness values associated
with program entities (e.g., basic blocks) based on coverage and the
output of test cases. More precisely, \sfl{} uses coverage information
of passing and failing test cases to identify likely faulty
statements. It produces on output a list of program entities ranked in
decreasing order of suspiciousness.
\ds{} and \sfl{} are complementary debugging techniques. Intuitively, \ds{} identifies
irrelevant parts of the code whereas \sfl{} ranks the relevant parts
of the code.

@@

This paper reports the results of a comprehensive study
to evaluate the impact of \ds{} to improve \sfl{}. The study involves
\numFaults{} faults from \numPrograms{} programs from the Defects4J
(D4J) dataset~\cite{just-defects4j-issta2014}, which is frequently
used to evaluated fault localization research. The intuition for the
\comb{} combination is that several highly ranked statements, albeit
covered by failing executions, may be unrelated to the fault. Prior
work reported promising results in this
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}
but they used non-representative set of subjects in their evaluation
or used less rigorours methods to assess improvement of techniques compared to those used
today~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.
The goal of this paper is to reassess whether the \comb{} combination
is worthwhile under the light of a more accurate metric and a larger
dataset. The D4J dataset is about twice as large than the biggest test
suite used in previous studies. It is worth noting that \acrAbrev{}
techniques should directly benefit from these results---either to
improve their results or to be aware they should not invest on this
integration. This study covers the following research questions:

@@

In the following, we illustrate the workflow of the \sfl{}+\cs{}
combination for this scenario. First, the combined technique picks
components $c_4$ and $c_3$, which appear at the top of the ranking,
for further analysis. (The cutoff point is user-defined.) Second, the
technique picks a failing test $t_2$ to slice the code.  Let us assume
that the slice obtained for the transaction $t_2$ is $\{c_2, c_5\}$,
\ie, it excludes components $c_4$ and $c_3$. Finally, the spectra and
ranking are updated. The right-side of Figure~\ref{fig:illustration}
shows the modified spectra and ranking after slicing test $t_2$
against $c_4$ and $c_3$. It is worth noting that the technique slices
the code for every failing tests. More precisely, the \sfl{}+\cs{} 
combination consists of four steps:\Sof{Should we specify that these steps are
performed for each version of the projects/defect?}
\begin{enumerate}
  \itemsep0em 
  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for 
  the input test suite;
  \item\label{step:susp-files} Select top $k$ most suspicious source 
  files, according to $R$;
  \item\label{step:compute-slice} Compute slicer for every suspicious
    file, obtained in Step~\ref{step:susp-files}, and every failing test;
  \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
    the slices obtained in Step~\ref{step:compute-slice} and recompute ranking.
\end{enumerate}

>>>>

% \author{
% First Author$^1$,
% Second Author$^2$,
% \\
% $^1$ First Affiliation\\
% $^2$ Second Affiliation\\
% %
% first@email.address,
% second@email.address,
% third@email.address
% }

@@

\hypersetup{draft} 
\begin{document}

@@

Dynamic Slicing (\ds{}) and Spectrum-Based Fault Localization (\sfl{})
are two very popular techniques that use different principles to
automate debugging. Dynamic
Slicing~\cite{Agrawal:1990:DPS:93542.93576} looks for the statements
in the code that influence some point of interest, such as the evaluation
of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
does not analyze code. It is a black-box statistical fault
localization method that computes suspiciousness values associated
with program entities (e.g., basic blocks) based on coverage and the
output of test cases. More precisely, \sfl{} uses coverage information
of passing and failing test cases to identify likely faulty
statements and produces on output a list of program entities ranked in
decreasing order of suspiciousness.
\ds{} and \sfl{} are complementary debugging techniques. Intuitively, \ds{} identifies
irrelevant parts of the code whereas \sfl{} ranks the relevant parts
of the code.

@@

This paper reports the results of a comprehensive study
to evaluate the impact of \ds{} to improve \sfl{}. The study involves
\numFaults{} faults from \numPrograms{} different programs comprised in the 
Defects4J (D4J) dataset~\cite{just-defects4j-issta2014}, which is frequently
used to evaluate fault localization research. The intuition for the
\comb{} combination is that several highly ranked statements, albeit
covered by failing executions, may be unrelated to the fault. Prior
work reported promising results in this
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}
but they used a non-representative set of subjects in their evaluation
or used less rigorous methods to assess improvement of techniques compared to those used
today~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.
The goal of this paper is to reassess whether the \comb{} combination
is worthwhile under the light of a more accurate metric and a larger
dataset. The D4J dataset is about twice as large than the biggest test
suite used in previous studies. It is worth noting that Automated
Program Repair techniques should directly benefit from these results---either to
improve their results or to be aware they should not invest on this
integration. This study covers the following research questions:

@@

In the following, we illustrate the workflow of the \sfl{}+\cs{}
combination for this scenario. First, the combined technique picks
components $c_4$ and $c_3$, which appear at the top of the ranking,
for further analysis. (The cutoff point is user-defined.) Second, the
technique picks a failing test $t_2$ to slice the code.  Let us assume
that the slice obtained for the transaction $t_2$ is $\{c_2, c_5\}$,
\ie, it excludes components $c_4$ and $c_3$. Finally, the spectra and
ranking are updated. The right-side of Figure~\ref{fig:illustration}
shows the modified spectra and ranking after slicing test $t_2$
against $c_4$ and $c_3$. It is worth noting that the technique slices
the code for every failing tests. More precisely, the \sfl{}+\cs{} 
combination consists of four steps:\Sof{Should we specify that these steps are
performed for each version of the projects/defect?}

\begin{enumerate}
  \itemsep0em 
  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for 
  the input test suite;
  \item\label{step:susp-files} Select top $k$ most suspicious source 
  files, according to $R$;
  \item\label{step:compute-slice} Compute slicer for every suspicious
    file, obtained in Step~\ref{step:susp-files}, and every failing test;
  \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
    the slices obtained in Step~\ref{step:compute-slice} and recompute ranking.
\end{enumerate}
